
%!TEX root = ../MainBody.tex

% 中英文摘要
\begin{CHSabstract}

	2014 年，ofo 共享单车出现再北大校园。2016 年，共享单车突然在中国变得火爆起来。随后，诸如此类的共享汽车，
	共享充电宝等如雨后春笋般出现。如今，共享经济已经流行了大约四年时间，共享经济的概念也已深入人心。当前市场
	上却鲜有与共享图书相关的平台出现。虽然市场上有很多二手交易平台，它们也提供图书的回收再出售，包括转卖。但是，
	却不是用户之间的直接图书共享，而且对二手书的回收要求较高，提供的交付方式也有限，基本是以快递的方式，交付成本
	较高。本文则尝试设计和开发了一套 Android 客户端的图书共享系统，以 Spring Boot 作为后台开发框架，Mysql 为后台
	数据库。实现了 Android 客户端的用户注册登录，发布图书，下达订单，沟通交流，支付订单，订单追踪等功能。该系统在
	校园内进行了推广试用，在推广的三天里，注册用户 52 人，发布图书 31 本，达成订单 11 单，获得了不错的运行效果。

\end{CHSabstract}
\begin{ENGabstract}
	In 2014, the ofo shared bicycles appeared on the campus of Peking University. In 2016, shared bicycles suddenly became popular in China. Then, such shared cars,
	Shared charging treasures have sprung up. Today, the sharing economy has been popular for about four years, and the concept of a shared economy has also gained popularity. Current market
	There are few platforms related to shared books. Although there are many second-hand trading platforms on the market, they also provide recycling and resale of books, including resale. but,
	It is not a direct book sharing between users, and the recycling requirements for second-hand books are high, and the delivery methods provided are limited, basically in the form of express delivery, delivery costs.
	Higher. This article attempts to design and develop a book sharing system for the Android client, with Spring Boot as the background development framework and Mysql as the background.
	Database. Implemented the Android client's user registration login, publishing books, placing orders, communication, payment orders, order tracking and other functions. The system is at
	On the campus, the promotion trial was carried out. During the three days of promotion, 52 registered users, 31 books were published, and 11 orders were reached, which achieved good results.
\end{ENGabstract}
